Tactics and Marks in Banach Mazur Games

### 2017-12-07 postdoctoral/k-markov-tactic-banach-mazur.tex
correct interpretation of Choquet game

  \begin{observation}
    When \(\mb P=\{(U,x):U\in T(X)\setminus\{\emptyset\},x\in U\}\)
    is ordered by \((U,x)\geq(V,y)\) whenever \(x\in V\subseteq U\)
    and \(W=\{\<U(n),x(n)\>_{n<\omega}\in\mb
    P^\downarrow:\bigcap_{n<\omega}U(n)\not=\emptyset\}\),
    then \(\bmPoGame{\mb P}{W}\) is almost the Choquet game, except the first
    player also gets to choose a point. Note \(W\) is closed under zipping.
  \end{observation}

>>>>

  \begin{observation}
    When \(\mb P=\{(U,x):U\in T(X)\setminus\{\emptyset\},x\in U\}\)
    is ordered by \((U,x)\geq(V,y)\) whenever \(x\in V\subseteq U\)
    and \(W=\{\<U(n),x(n)\>_{n<\omega}\in\mb
    P^\downarrow:\bigcap_{n<\omega}U(n)\not=\emptyset\}\),
    then \(\bmPoGame{\mb P}{W}\) is almost the Choquet game, except the second
    player also gets to choose a point. Note \(W\) is closed under zipping.
  \end{observation}
